Scikit-learn: machine learning without learning the machinery

### 2014-07-04 article.tex
wording

Here, we asked the estimator to predict whether the reviews were positive
The first review is predicted as being negative (0),
while the second is positive (1). We have
anecdotal evidence that the classifier works. To get a measure for the
classifier's accuracy we retrain it in a cross-validation scheme.
This yields the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}

>>>>

Here, we asked the estimator to predict whether the reviews were
positive.
The first review is predicted as being negative (0),
while the second is positive (1). We have
anecdotal evidence that the classifier works. To get a measure for the
classifier's accuracy we retrain it in a cross-validation scheme.
This yields the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}
